---
title: "Generalized Test of MODMCMC"
author: "Michael Najarro +Patty Oikawa"
date: "6/27/2021"
output: html_document:
    keep_md: yes
---

# Introduction

The underlying goal of this project is to evaluate whether the MEM-PEPRMT model can predict coastal wetland methane emissions on a national scale by implementing the model on wetland data from multiple sites.

However, to run this model, parameters involved in physical chemistry within PEPRMT must be parameterized.


# Goal
This script is a test run of implementing the package FME's function `modMCMC`, which implements a delayed rejection adaptive monte carlo markov chain algorithm, to estimate theta parameters for PEPRMT upon a multi site data set.




# The Process

```{r, echo=FALSE, message=FALSE}
library(pacman)
p_load(R.matlab,
       here,
       tidyverse,
       magrittr,
       FME,
       tictoc,
       beepr,
       Metrics,
       gridExtra)
```

## 1. Build error data set

Estimating parameters for PEPRMT requires having eddy covariance data in order to calculate an error term (or vector of terms) for DRAM. The data is comprised of a data frame containing the methane, daily integral error (gap filled), and random error from Eddy Covariance Towers.

For MEM-PEPRMT, we will calculate a sum of squares on the error data, which will later applied to the DRAM parameter space selection distribution. 

Unfortunately error data exists only for Eden landing. To create error data for Rush Ranch and St. Jones, I will sample with replacement EL.

For each day that exists within a given data set, there should exist three error values: ydata, gpf, and re.

first identify the number of days of data per site, by recording the number of rows per site.

```{r}
# #load in the data. 

EL_RR_data <- read.csv("All_param_sites_master_NO3_corr_20220309.csv", header=TRUE) %>% 
 dplyr::select(1:12) 
# 


#New data all sites in 1 spreadsheet
EL_RR_De_data <- read.csv("All_param_sites_master_NO3_corr_20211206_GPP.csv", header=TRUE) %>% 
  dplyr::select(1:18) 
summary(EL_RR_De_data)
str(EL_RR_De_data)
# days measured for each site.
#table(as.character(initial_data$site))
table(as.character(EL_RR_De_data$site))
```

There are 873, 512, and 366, measures for Eden Landing, Rush Ranch, and St. Jones.  Let's convert the site to a numerical value, which will become a critical component for running PEPRMT.

```{r echo=FALSE}
#initial_data$site <- as.numeric(initial_data$site)
EL_RR_De_data$site <- as.numeric(factor(EL_RR_De_data$site))
summary(EL_RR_De_data)
```


Given that we have measures of error for Eden Landing, I must now generate more data for each column of the error data set. I'll build upon the Eden Landing data by extending it columns out. 

```{r}
# #import EL error data.

global_errors <- read.csv("All_param_sites_master_NO3_corr_20211206_GPP.csv", header=TRUE) %>% 
 dplyr::select(13:15) 
#global_errors<-EL_RR_De_data[c(13:15)]

```


## 2. Test run of the SS script

Now, that error data exists for all three sites merged into one data frame, I can calculate a sum of squares upon the data by running the `SS PEPRMT CH4` script.


```{r}
#determining LUE for each site

#Best to keep the umol unit
LUE_gC_MJ_Edn_umol=mean(EL_RR_De_data$GPP_gC_m2_day[1:1217]/EL_RR_De_data$PAR_daily_ave_umol_m2_day[1:1217])
LUE_gC_MJ_Srr_umol=mean(EL_RR_De_data$GPP_gC_m2_day[1218:2871]/EL_RR_De_data$PAR_daily_ave_umol_m2_day[1218:2871])
EL_RR_De_data$PAR_daily_ave_umol_m2_day[2872]<-EL_RR_De_data$PAR_daily_ave_umol_m2_day[2871]
LUE_gC_MJ_Stj_umol=mean(EL_RR_De_data$GPP_gC_m2_day[2872:3967]/EL_RR_De_data$PAR_daily_ave_umol_m2_day[2872:3967])
#Now create a LUE column for entire dataset that uses this growing season mean LUE for each site
EL_RR_De_data$LUE <-EL_RR_De_data$Wetland_age_years*0
EL_RR_De_data$LUE[1:1217] <-EL_RR_De_data$LUE[1:1217]+LUE_gC_MJ_Edn_umol*-1
EL_RR_De_data$LUE[1218:2871] <-EL_RR_De_data$LUE[1218:2871]+LUE_gC_MJ_Srr_umol*-1
EL_RR_De_data$LUE[2872:3967] <-EL_RR_De_data$LUE[2872:3967]+LUE_gC_MJ_Stj_umol*-1


```







```{r}
# bring in required inputs
#: global errors should be in your environment, which is the full error data set.
#error_set <- global_errors
  
source('PEPRMT_final_sys_CO2_GPP_param.R')

#

     # run peprmt Reco
    #theta <- c(1, 1, 0, 0)
    #theta <-c(1.015387 ,  1.008252, 110.973354,  99.983830)
     theta <-c(1,1, 110.973354,  99.983830)
    GPP_mod_RR <- PEPRMT_final_sys_CO2_GPP_param(theta,
                                           data = EL_RR_De_data)

  #make new data matrix for plotting
  EL_RR_De_data_results <- read.csv("All_param_sites_master_NO3_corr_20211206_GPP.csv", header=TRUE) %>% 
  dplyr::select(1:15) 
 
  EL_RR_De_data_results$GPP_mod <- GPP_mod_RR
  
  #PLOT new RESULTS  2015-17
  #eden
    # ggplot(data = EL_RR_De_data_results, mapping = aes(x = Day_of_year, y = CH4_mod)) 
    # geom_point(alpha = 0.1, color = "blue")
    
    plot(EL_RR_De_data_results$Day_of_year[1:1217],EL_RR_De_data_results$GPP_mod[1:1217], type="b", pch=19, col="red", xlab="DOY", ylab="CH4 (gC m-2 d-1)")
# Add a line
lines(EL_RR_De_data_results$Day_of_year[1:1217], EL_RR_De_data_results$GPP_gC_m2_day[1:1217], type="l", pch=18, col="blue")#, type="b", lty=2)
# Add a legend
legend(1, 95, legend=c("mod", "obs"),
       col=c("red", "blue"))#, lty=1:2, cex=0.8)
RMSE_GPP_mod_Edn_prior <- rmse(EL_RR_De_data_results$GPP_mod[1:1217], EL_RR_De_data_results$GPP_gC_m2_day[1:1217])
#RR
    # ggplot(data = EL_RR_De_data_results, mapping = aes(x = Day_of_year, y = CH4_mod)) 
    # geom_point(alpha = 0.1, color = "blue")
    
    plot(EL_RR_De_data_results$Day_of_year[1218:2871],EL_RR_De_data_results$GPP_mod[1218:2871], type="b", pch=19, col="red", xlab="DOY", ylab="CH4 (gC m-2 d-1)")
# Add a line
lines(EL_RR_De_data_results$Day_of_year[1218:2871], EL_RR_De_data_results$GPP_gC_m2_day[1218:2871], type="l", pch=18, col="blue")#, type="b", lty=2)
# Add a legend
legend(1, 95, legend=c("mod", "obs"),
       col=c("red", "blue"))#, lty=1:2, cex=0.8)
RMSE_GPP_mod_Srr_prior <- rmse(EL_RR_De_data_results$GPP_mod[1218:2871], EL_RR_De_data_results$GPP_gC_m2_day[1218:2871])
#Stj
    # ggplot(data = EL_RR_De_data_results, mapping = aes(x = Day_of_year, y = CH4_mod)) 
    # geom_point(alpha = 0.1, color = "blue")
    
    plot(EL_RR_De_data_results$Day_of_year[2872:3967],EL_RR_De_data_results$GPP_mod[2872:3967], type="b", pch=19, col="red", xlab="DOY", ylab="CH4 (gC m-2 d-1)")
# Add a line
lines(EL_RR_De_data_results$Day_of_year[2872:3967], EL_RR_De_data_results$GPP_gC_m2_day[2872:3967], type="l", pch=18, col="blue")#, type="b", lty=2)
# Add a legend
legend(1, 95, legend=c("mod", "obs"),
       col=c("red", "blue"))#, lty=1:2, cex=0.8)

RMSE_GPP_mod_Stj_prior <- rmse(EL_RR_De_data_results$GPP_mod[2872:3967], EL_RR_De_data_results$GPP_gC_m2_day[2872:3967])

#write_csv(EL_RR_De_data_results,"data_sets/final_model_results.csv")

```




```{r}
source('SS_PEPRMT_GPP.R')

saveRDS(EL_RR_De_data, file = "EL_RR_De_data.rds")
#theta <- c(0.5,0.5, 0, 0)
theta <-c(1,1, 110.973354,  99.983830)
# run the sum of squares script as a test
ss_global <- ss_GPP(theta = theta,
   y = global_errors)


#use for troubleshooting SS code
# y = global_errors
# plot(ydata)
# plot(mod)
# plot(ss1, ylim=c(0,1))
# plot(y$daily_wm_gf_error,ylim=c(0,0.1))
# plot(y$daily_wm_re_error)


```


## 3. FME: modMCMC function

Here we will open the package FME and execute the 
method `modMCMC`, which will run a delayed-rejection, adaptive Monte Carlo Markov Chain, Metroplolis- Hastings Algorithm.

```{r}
# run FME
tic()
paramod <- modMCMC(f = ss_GPP,
        p = theta,
        y = global_errors,
        jump = .01,  
        lower = c(0,1,-20, -50),
        upper = c(5,5,200, 300),
        prior = NULL,
        var0 = NULL,
        wvar0 = NULL, 
        n0 = NULL,
        niter = 200000,
        outputlength = 200000,
        burninlength = 50000,
        updatecov = 100,
        covscale = 2.4^2/length(theta),
        ntrydr = 2,
        drscale = NULL,
        verbose = TRUE)
toc()
beepr::beep(sound=2)
```

```{r}
#Save and load paramod depending on date of run
saveRDS(paramod,"paramod_20221115.rds")

paramod<-readRDS("paramod_20221115.rds")

#plot best parameter set
theta_best <- paramod$bestpar

#test how model performs
source('PEPRMT_final_sys_CO2_GPP_param.R')
  

  #5. execute PEPRMT CH4

  y_model <- PEPRMT_final_sys_CO2_GPP_param(theta = theta_best,
                                      data = EL_RR_De_data)
  #add it onto results matrix
  EL_RR_De_data_results$GPP_mod_best <- y_model
  
  #PLOT new RESULTS  2015-17
  #eden
    # ggplot(data = EL_RR_De_data_results, mapping = aes(x = Day_of_year, y = CH4_mod_best)) 
    # geom_point(alpha = 0.1, color = "blue")
  par(mfrow=c(2,2))  
    plot(EL_RR_De_data_results$Day_of_year[1:1217],EL_RR_De_data_results$GPP_mod_best[1:1217], type="b", pch=19, col="red", xlab="DOY", ylab="GPP (gC m-2 d-1)", ylim=c(-15, 1))
# Add a line
lines(EL_RR_De_data_results$Day_of_year[1:1217], EL_RR_De_data_results$GPP_gC_m2_day[1:1217]+1, type="l", pch=18, col="blue", ylim=c(-15, 1))#, type="b", lty=2)
# Add a legend
legend(1, 95, legend=c("mod", "obs"),
       col=c("red", "blue"))#, lty=1:2, cex=0.8)

RMSE_GPP_mod_Edn <- rmse(EL_RR_De_data_results$GPP_mod_best[1:1217], EL_RR_De_data_results$GPP_gC_m2_day[1:1217])
#RR
    # ggplot(data = EL_RR_De_data_results, mapping = aes(x = Day_of_year, y = CH4_mod_best)) 
    # geom_point(alpha = 0.1, color = "blue")
    
    plot(EL_RR_De_data_results$Day_of_year[1218:2871],EL_RR_De_data_results$GPP_mod_best[1218:2871], type="b", pch=19, col="red", xlab="DOY", ylab="GPP (gC m-2 d-1)", ylim=c(-15, 1))
# Add a line
lines(EL_RR_De_data_results$Day_of_year[1218:2871], EL_RR_De_data_results$GPP_gC_m2_day[1218:2871], type="l", pch=18, col="blue", ylim=c(-15, 1))#, type="b", lty=2)
# Add a legend
legend(1, 95, legend=c("mod", "obs"),
       col=c("red", "blue"))#, lty=1:2, cex=0.8)

RMSE_GPP_mod_Srr <- rmse(EL_RR_De_data_results$GPP_mod_best[1218:2871], EL_RR_De_data_results$GPP_gC_m2_day[1218:2871])

#Stj
    # ggplot(data = EL_RR_De_data_results, mapping = aes(x = Day_of_year, y = CH4_mod_best)) 
    # geom_point(alpha = 0.1, color = "blue")
    
    plot(EL_RR_De_data_results$Day_of_year[2872:3967],EL_RR_De_data_results$GPP_mod_best[2872:3967], type="b", pch=19, col="red", xlab="DOY", ylab="GPP (gC m-2 d-1)", ylim=c(-15, 1))
# Add a line
lines(EL_RR_De_data_results$Day_of_year[2872:3967], EL_RR_De_data_results$GPP_gC_m2_day[2872:3967], type="l", pch=18, col="blue", ylim=c(-15, 1))#, type="b", lty=2)
# Add a legend
legend(1, 95, legend=c("mod", "obs"),
       col=c("red", "blue"))#, lty=1:2, cex=0.8)

RMSE_GPP_mod_Stj <- rmse(EL_RR_De_data_results$GPP_mod_best[2872:3967], EL_RR_De_data_results$GPP_gC_m2_day[2872:3967])
```




#investigate SS
```{r}
hist(paramod$SS)
plot(paramod$SS)

#bring in script
source("SS_PEPRMT_GPP.R")

# run the sum of squares script as a test
ss_global <- ss_GPP(theta = theta_best,
   y = global_errors)

saveRDS(paramod,file="paramod.rds")
paramod<-readRDS("paramod.rds")
```




## 5. Plot markov chains per parameter

here i plot each parameter and then zoom in on the last 5% of jump steps to determine the limit, or to where the posterior distribution $\pi(x)$ converges per parameter.

```{r}
df_thetas <- as.data.frame(paramod$pars)
colnames(df_thetas) <- c("t1", 
                          "t2",
                          "t3",
                          "t4")

df_thetas <- df_thetas %>%
        mutate(step = c(1:nrow(df_thetas))) %>%
        pivot_longer(.,
                     c(t1,
                       t2,
                       t3,
                       t4),
                     names_to = "parameter",
                     values_to = "state")

#Plot each parameter
ggplot(data =df_thetas,
       mapping=aes(x=step,
                   y =state)) +
        geom_line(mapping=aes(col=parameter))

# Now plot up to the last 5% of the step values
lv <- as.numeric(max(df_thetas$step)-.05*max(df_thetas$step))
uv <- as.numeric(max(df_thetas$step))

ggplot(data =df_thetas,
       mapping=aes(x=step,
                   y=state)) +
        geom_line(mapping=aes(col=parameter)) +
        coord_trans(xlim=c(lv,uv))
```
Checking for MCMC convergence
http://docs.zeligproject.org/articles/diagnostics.html
Geweke Diagnostic
The Geweke diagnostic tests the null hypothesis that the Markov chain is in the stationary distribution and produces z-statistics for each estimated parameter.

Heidelberger-Welch Diagnostic
The Heidelberger and Welch diagnostic first tests the null hypothesis that the Markov Chain is in the stationary distribution and produces p-values for each estimated parameter. Calling this diagnostic also produces output that indicates whether the mean of a marginal posterior distribution can be estimated with sufficient precision, assuming that the Markov Chain is in the stationary distribution

Raftery-Lewis Diagnostic
The Raftery and Lewis diagnostic indicates how long the Markov Chain should run before considering draws from the marginal posterior distributions sufficiently representative of the stationary distribution.

```{r}
#checking for convergence
#GEWEKE
#Geweke (1992) proposed a convergence diagnostic for Markov chains based on a test for equality of the means of the first and last part of a Markov chain (by default the first 10% and the last 50%). If the samples are drawn from the stationary distribution of the chain, the two means are equal and Geweke's statistic has an asymptotically standard normal distribution
#if all the parameters have a pvalue >0.05 then we can assume the first 10% of the chain is burn in
geweke.diag(paramod$pars, frac1=0.1, frac2=0.5) #if all p values are > 0.05 passes
```

```{r}
#HEIDEL
#The convergence test uses the Cramer-von-Mises statistic to test the null hypothesis that the sampled values come from a stationary distribution. The test is successively applied, firstly to the whole chain, then after discarding the first 10%, 20%, … of the chain until either the null hypothesis is accepted, or 50% of the chain has been discarded. The latter outcome constitutes `failure' of the stationarity test and indicates that a longer MCMC run is needed. If the stationarity test is passed, the number of iterations to keep and the number to discard are reported.
heidel.diag(paramod$pars)#Check if all parameters pass, if not a longer chain may be needed

```

```{r}
#RAFTERY
#If the number of iterations in data is too small, an error message is printed indicating the minimum length of pilot run. The minimum length is the required sample size for a chain with no correlation between consecutive samples. Positive autocorrelation will increase the required sample size above this minimum value. An estimate I (the `dependence factor') of the extent to which autocorrelation inflates the required sample size is also provided. Values of I larger than 5 indicate strong autocorrelation which may be due to a poor choice of starting value, high posterior correlations or `stickiness' of the MCMC algorithm.
raftery.diag(paramod$pars)


```

```{r}
#make box plots of last 10,000 parameter sets


final_parameter_set = paramod$pars
#for longer chains
final_parameter_set <- final_parameter_set[135001:145000, ]
#for shorter chains
#final_parameter_set <- final_parameter_set[35001:45000, ]

boxplot(final_parameter_set,data=final_parameter_set, main="parameter stability",
   xlab="parameter", ylab="parameter values")#,ylim=c(0.75,1.3))
```



```{r gpp_param_distr, dev = c("jpg")}

#tiff("gpp_param_distr.tiff")
#Best to just screenshot this figure and save 
par(mfrow=c(2,2))
hist1<- hist(final_parameter_set[,1],main="",
xlab=expression('a'['0']))
text(0.6, 2300, cex = 1, bquote(paste((a))))#cex changes font size
hist2<-hist(final_parameter_set[,2],main="",
xlab=expression('a'['1']))
text(1.1, 4900, cex = 1, bquote(paste((b))))#cex changes font size
hist3<-hist(final_parameter_set[,3]+30,main="",
xlab=expression('H'['a']* ' (kJ mol'^'-1'* ')'))
text(65, 1000, cex = 1, bquote(paste((c))))#cex changes font size
hist4<-hist(final_parameter_set[,4]+100,main="",
xlab=expression('H'['d']* ' (kJ mol'^'-1' * ')'))
text(55, 800, cex = 1, bquote(paste((d))))#cex changes font size
#dev.off()


# head(final_parameter_set)
# final_param_long <- final_parameter_set %>% 
#   as.data.frame() %>%
#   pivot_longer(cols = everything(), names_to = "params", values_to= "estimate")
# 
# head(final_param_long)
# 
# final_param_plot <- ggplot(final_param_long, aes(x = estimate)) +
#   geom_histogram() +
#   facet_wrap(~params)
# final_param_plot

```

```{r}


#identify median and CI for ea parameter
theta_med <- apply(final_parameter_set,2, function(x) median(x))
cil_theta <- apply(final_parameter_set,2, function(x) quantile(x, 0.025))
ciu_theta <- apply(final_parameter_set, 2, function(x) quantile(x, 0.975))


#are parameters correlated
r2_theta1_2 <- cor(final_parameter_set[ ,1], final_parameter_set[ ,2])
r2_theta1_3 <- cor(final_parameter_set[ ,1], final_parameter_set[ ,3])
r2_theta1_4 <- cor(final_parameter_set[ ,1], final_parameter_set[ ,4])
r2_theta2_3 <- cor(final_parameter_set[ ,2], final_parameter_set[ ,3])
r2_theta2_4 <- cor(final_parameter_set[ ,2], final_parameter_set[ ,4])
r2_theta3_4 <- cor(final_parameter_set[ ,3], final_parameter_set[ ,4])

model_theta_1_2 <- lm(final_parameter_set[ ,1] ~ final_parameter_set[ ,2])
summary(model_theta_1_2)
#theta 1 and 2 are correlated byt the r2 is low =0.02

model_theta_1_3 <- lm(final_parameter_set[ ,1] ~ final_parameter_set[ ,3])
summary(model_theta_1_3)
#theta 1 and 3 are correlated r2=0.43

model_theta_1_4 <- lm(final_parameter_set[ ,1] ~ final_parameter_set[ ,4])
summary(model_theta_1_4)
#theta 1 and 4 are correlated but r2 is low 0.09

model_theta_2_3 <- lm(final_parameter_set[ ,2] ~ final_parameter_set[ ,3])
summary(model_theta_2_3)
#theta 2 and 3 are correlated but r2 is low 0.07

model_theta_2_4 <- lm(final_parameter_set[ ,2] ~ final_parameter_set[ ,4])
summary(model_theta_2_4)
#theta 2 and 4 are correlated but r2 is low 0.01


model_theta_3_4 <- lm(final_parameter_set[ ,3] ~ final_parameter_set[ ,4])
summary(model_theta_3_4)
#theta 3 and 4 are correlated  r2 =0.64 

 par(mfrow=c(3,3))  
plot(final_parameter_set[ ,1],final_parameter_set[ ,2],type="b", pch=19, col="red", xlab="theta 1", ylab="theta 2")
plot(final_parameter_set[ ,1],final_parameter_set[ ,3],type="b", pch=19, col="red", xlab="theta 1", ylab="theta 3")
plot(final_parameter_set[ ,1],final_parameter_set[ ,4],type="b", pch=19, col="red", xlab="theta 1", ylab="theta 4")
plot(final_parameter_set[ ,2],final_parameter_set[ ,3],type="b", pch=19, col="red", xlab="theta 2", ylab="theta 3")
plot(final_parameter_set[ ,2],final_parameter_set[ ,4],type="b", pch=19, col="red", xlab="theta 2", ylab="theta 4")
plot(final_parameter_set[ ,3],final_parameter_set[ ,4],type="b", pch=19, col="red", xlab="theta 3", ylab="theta 4")
```






```{r}
theta_med
theta_median <- c(0.7479271,   1.0497113, 149.4681710,  94.4532674 )
#make output
theta_median_actual<-theta_median
theta_median_actual[1] <- theta_median[1]
theta_median_actual[2] <- theta_median[2]
theta_median_actual[3] <- theta_median[3]+30
theta_median_actual[4] <- theta_median[4]+100
#test how model performs
source('./PEPRMT_Scripts/PEPRMT_final_sys_CO2_GPP_param.R')
  

  #5. execute PEPRMT CH4

  y_model <- PEPRMT_final_sys_CO2_GPP_param(theta = theta_median,
                                      data = EL_RR_De_data)
  #add it onto results matrix
  EL_RR_De_data_results$GPP_mod_best <- y_model
  
  #PLOT new RESULTS  2015-17
  #eden
    # ggplot(data = EL_RR_De_data_results, mapping = aes(x = Day_of_year, y = CH4_mod_best)) 
    # geom_point(alpha = 0.1, color = "blue")
  par(mfrow=c(2,2))  
    plot(EL_RR_De_data_results$Day_of_year[1:1217],EL_RR_De_data_results$GPP_mod_best[1:1217], type="b", pch=19, col="red", xlab="DOY", ylab="GPP (gC m-2 d-1)", ylim=c(-15, 1))
# Add a line
lines(EL_RR_De_data_results$Day_of_year[1:1217], EL_RR_De_data_results$GPP_gC_m2_day[1:1217]+1, type="l", pch=18, col="blue", ylim=c(-15, 1))#, type="b", lty=2)
# Add a legend
legend(1, 95, legend=c("mod", "obs"),
       col=c("red", "blue"))#, lty=1:2, cex=0.8)

RMSE_GPP_mod_Edn <- rmse(EL_RR_De_data_results$GPP_mod_best[1:1217], EL_RR_De_data_results$GPP_gC_m2_day[1:1217])
#RR
    # ggplot(data = EL_RR_De_data_results, mapping = aes(x = Day_of_year, y = CH4_mod_best)) 
    # geom_point(alpha = 0.1, color = "blue")
    
    plot(EL_RR_De_data_results$Day_of_year[1218:2871],EL_RR_De_data_results$GPP_mod_best[1218:2871], type="b", pch=19, col="red", xlab="DOY", ylab="GPP (gC m-2 d-1)", ylim=c(-15, 1))
# Add a line
lines(EL_RR_De_data_results$Day_of_year[1218:2871], EL_RR_De_data_results$GPP_gC_m2_day[1218:2871], type="l", pch=18, col="blue", ylim=c(-15, 1))#, type="b", lty=2)
# Add a legend
legend(1, 95, legend=c("mod", "obs"),
       col=c("red", "blue"))#, lty=1:2, cex=0.8)

RMSE_GPP_mod_Srr <- rmse(EL_RR_De_data_results$GPP_mod_best[1218:2871], EL_RR_De_data_results$GPP_gC_m2_day[1218:2871])

#Stj
    # ggplot(data = EL_RR_De_data_results, mapping = aes(x = Day_of_year, y = CH4_mod_best)) 
    # geom_point(alpha = 0.1, color = "blue")
    
    plot(EL_RR_De_data_results$Day_of_year[2872:3967],EL_RR_De_data_results$GPP_mod_best[2872:3967], type="b", pch=19, col="red", xlab="DOY", ylab="GPP (gC m-2 d-1)", ylim=c(-15, 1))
# Add a line
lines(EL_RR_De_data_results$Day_of_year[2872:3967], EL_RR_De_data_results$GPP_gC_m2_day[2872:3967], type="l", pch=18, col="blue", ylim=c(-15, 1))#, type="b", lty=2)
# Add a legend
legend(1, 95, legend=c("mod", "obs"),
       col=c("red", "blue"))#, lty=1:2, cex=0.8)

RMSE_GPP_mod_Stj <- rmse(EL_RR_De_data_results$GPP_mod_best[2872:3967], EL_RR_De_data_results$GPP_gC_m2_day[2872:3967])

```

```{r}
#run the model on all 10,000 sets and plot means and 95% CI

source('./PEPRMT_Scripts/PEPRMT_final_sys_CO2_GPP_param.R')

GPP_mod <- NULL

#--loop for running model 10,000 times---
  for(t in 1:length(final_parameter_set[ ,1])) {

  
  #5. execute PEPRMT CH4
  y_model<- PEPRMT_final_sys_CO2_GPP_param(theta = final_parameter_set[t , ],
                           data = EL_RR_De_data)
  mod_result <- y_model
  GPP_mod <- cbind(GPP_mod, mod_result)
  }

GPP_mod <- as.data.frame(GPP_mod)

## Transpose data.frame so that columns are time points and rows are samples from posterior
GPP_mod2 <- GPP_mod %>%
  t() %>%
  as.data.frame() %>%
  slice(1:10000)

## Calculate median and 95% credible intervals
## Each of these objects are vectors of length 3967
medianGPP <- apply(GPP_mod2, 2, median)
cilGPP <- apply(GPP_mod2, 2, function(x) quantile(x, 0.025))
ciuGPP <- apply(GPP_mod2, 2, function(x) quantile(x, 0.975))

## Put the summary stats together, with column of time points
library(lubridate)
GPPmod_summary <- data.frame(time = 1:length(medianGPP), 
                             median = medianGPP,
                             cil = cilGPP,
                             ciu = ciuGPP)

#For a ggplot figure with line and shaded region:
GPPModelPlot <- ggplot(GPPmod_summary, aes(x = time, y = median)) +
  geom_ribbon(aes(ymin = cil, ymax = ciu), fill = "grey70", alpha = 1) + # shaded region
  geom_line(color = "black") + # line
  ## To edit the x and y axes
  scale_x_continuous("Time") +
  scale_y_continuous("GPP") +
  ## To make the plot look prettier
  theme_bw(base_size = 12) +
  theme(axis.line = element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(colour = "black"),
        panel.background = element_blank(),
        legend.position = "none")
GPPModelPlot


#add to results file for plotting
EL_RR_De_data_results$GPP_mod_final<-GPPmod_summary[,2]
EL_RR_De_data_results$cil<-GPPmod_summary[,3]
EL_RR_De_data_results$ciu<-GPPmod_summary[,4]

## Hard to see the CI 
## Eden Landing Plot

edn<-ggplot(EL_RR_De_data_results[1:1217,], aes(Day_of_year)) +
  geom_ribbon(aes(ymin = cil, ymax = ciu), fill = "grey50", alpha = 1) + # shaded region
  geom_line(aes(x = Day_of_year, y = GPP_mod_final))+
  geom_line(aes(y = GPP_gC_m2_day+1), color = "red")+
  ## To edit the x and y axes
  #scale_x_continuous("") +
  #scale_y_continuous("") +
  labs(x = "", y="          ") +
  geom_text(x=20, y=0, label="(a)")+
  ## To make the plot look prettier
  theme_bw(base_size = 12) +
  theme(axis.line = element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(colour = "black"),
        panel.background = element_blank(),
        legend.position = "center")


#Rush Ranch
RR<-ggplot(EL_RR_De_data_results[1218:2871,], aes(Day_of_year)) +
  geom_ribbon(aes(ymin = cil, ymax = ciu), fill = "grey50", alpha = 1) + # shaded region
  geom_line(aes(y = GPP_mod_final))+
  geom_line(aes(y = GPP_gC_m2_day, color = "red"))+
 
  ## To edit the x and y axes
  #scale_x_continuous("") +
  #scale_y_continuous("") +
  labs(x = "", y=bquote('GPP '~ (gC ~ m^-2 ~ d^-1))) +

  geom_text(x=30, y=-2, label="(b)")+
  ## To make the plot look prettier
  theme_bw(base_size = 12) +
  theme(axis.line = element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(colour = "black"),
        panel.background = element_blank(),
        legend.position = "center") 

#Delaware
Stj<-ggplot(EL_RR_De_data_results[2872:3967,], aes(Day_of_year)) +
  geom_ribbon(aes(ymin = cil, ymax = ciu), fill = "grey50", alpha = 1) + # shaded region
  geom_line(aes(y = GPP_mod_final))+
  geom_line(aes(y = GPP_gC_m2_day, color = "red"))+
  ## To edit the x and y axes
  #scale_x_continuous("") +
  #scale_y_continuous("") +
  labs(x = "Continuous day of year", y="          ") +
  geom_text(x=-25, y=-1, label="(c)")+
  ## To make the plot look prettier
  theme_bw(base_size = 12) +
  theme(axis.line = element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(colour = "black"),
        panel.background = element_blank(),
        legend.position = "center") 


```





```{r}
#Run stats on final model results
EL_RR_De_data_results$medianGPP <- medianGPP
medianGPP<-EL_RR_De_data_results$medianGPP


RMSE_GPP_mod_Edn <- rmse(medianGPP[1:1217], EL_RR_De_data_results$GPP_gC_m2_day[1:1217])
RMSE_GPP_mod_Srr <- rmse(medianGPP[1218:2871], EL_RR_De_data_results$GPP_gC_m2_day[1218:2871])
RMSE_GPP_mod_Stj <- rmse(medianGPP[2872:3967], EL_RR_De_data_results$GPP_gC_m2_day[2872:3967])

#Normalized RMSE dimensionless metric of accuracy of model against SD of obs
SD_GPP_Edn <-sd(EL_RR_De_data_results$GPP_gC_m2_day[1:1217])
SD_GPP_Srr <- sd(EL_RR_De_data_results$GPP_gC_m2_day[1218:2871])
SD_GPP_Stj <- sd(EL_RR_De_data_results$GPP_gC_m2_day[2872:3967])

N_RMSE_GPP_mod_Edn <- RMSE_GPP_mod_Edn/SD_GPP_Edn
N_RMSE_GPP_mod_Srr <- RMSE_GPP_mod_Srr/SD_GPP_Srr
N_RMSE_GPP_mod_Stj <- RMSE_GPP_mod_Stj/SD_GPP_Stj
#Pearson's correlation coefficient
r_Edn <- cor(EL_RR_De_data_results$GPP_gC_m2_day[1:1217]+1, medianGPP[1:1217])
r_Srr <- cor(EL_RR_De_data_results$GPP_gC_m2_day[1218:2871], medianGPP[1218:2871])
r_Stj <- cor(EL_RR_De_data_results$GPP_gC_m2_day[2872:3967], medianGPP[2872:3967])

model_Edn <- lm(GPP_gC_m2_day[1:1217]+1 ~ medianGPP[1:1217], data=EL_RR_De_data_results)
summary(model_Edn)
model_Srr <- lm(GPP_gC_m2_day[1218:2871] ~ medianGPP[1218:2871], data=EL_RR_De_data_results)
summary(model_Srr)
model_Stj <- lm(GPP_gC_m2_day[2872:3967] ~ medianGPP[2872:3967], data=EL_RR_De_data_results)
summary(model_Stj)

library(gridExtra)

#Annual error in g C m-2 y-1
annual_error_Edn_year1 <- (tail(cumsum(medianGPP[1:319]),1)-tail(cumsum(EL_RR_De_data_results$GPP_gC_m2_day[1:319]),1))
annual_error_Edn_year2 <- (tail(cumsum(medianGPP[320:684]),1)-tail(cumsum(EL_RR_De_data_results$GPP_gC_m2_day[320:684]),1))
annual_error_Edn_year3 <- (tail(cumsum(medianGPP[685:1050]),1)-tail(cumsum(EL_RR_De_data_results$GPP_gC_m2_day[685:1050]),1))
ave_annual_error_Edn <- (annual_error_Edn_year1+annual_error_Edn_year2+annual_error_Edn_year3)/3

annual_error_Srr_year1 <- (tail(cumsum(medianGPP[1218:1512]),1)-tail(cumsum(EL_RR_De_data_results$GPP_gC_m2_day[1218:1512]),1))
annual_error_Srr_year2 <- (tail(cumsum(medianGPP[1513:1877]),1)-tail(cumsum(EL_RR_De_data_results$GPP_gC_m2_day[1513:1877]),1))
annual_error_Srr_year3 <- (tail(cumsum(medianGPP[1878:2243]),1)-tail(cumsum(EL_RR_De_data_results$GPP_gC_m2_day[1878:2243]),1))
annual_error_Srr_year4 <- (tail(cumsum(medianGPP[2244:2608]),1)-tail(cumsum(EL_RR_De_data_results$GPP_gC_m2_day[2244:2608]),1))
annual_error_Srr_year5 <- (tail(cumsum(medianGPP[2609:2871]),1)-tail(cumsum(EL_RR_De_data_results$GPP_gC_m2_day[2609:2871]),1))
ave_annual_error_Srr <- (annual_error_Srr_year1+annual_error_Srr_year2+annual_error_Srr_year3+annual_error_Srr_year4+annual_error_Srr_year5)/5

annual_error_Stj_year1 <- (tail(cumsum(medianGPP[2872:3236]),1)-tail(cumsum(EL_RR_De_data_results$GPP_gC_m2_day[2872:3236]),1))
annual_error_Stj_year2 <- (tail(cumsum(medianGPP[3237:3602]),1)-tail(cumsum(EL_RR_De_data_results$GPP_gC_m2_day[3237:3602]),1))
annual_error_Stj_year3 <- (tail(cumsum(medianGPP[3603:3967]),1)-tail(cumsum(EL_RR_De_data_results$GPP_gC_m2_day[3603:3967]),1))
ave_annual_error_Stj <- (annual_error_Stj_year1+annual_error_Stj_year2+annual_error_Stj_year3)/3

#Annual error %
annual_error_Edn_percent_year1 <- (min(cumsum(medianGPP[1:319]))-min(cumsum(EL_RR_De_data_results$GPP_gC_m2_day[1:319])))/min(cumsum(EL_RR_De_data_results$GPP_gC_m2_day[1:319]))*100
annual_error_Edn_percent_year2 <- (min(cumsum(medianGPP[320:684]))-min(cumsum(EL_RR_De_data_results$GPP_gC_m2_day[320:684])))/min(cumsum(EL_RR_De_data_results$GPP_gC_m2_day[320:684]))*100
annual_error_Edn_percent_year3 <- (min(cumsum(medianGPP[685:1050]))-min(cumsum(EL_RR_De_data_results$GPP_gC_m2_day[685:1050])))/min(cumsum(EL_RR_De_data_results$GPP_gC_m2_day[685:1050]))*100
ave_annual_error_Edn <- (annual_error_Edn_percent_year1+annual_error_Edn_percent_year2+annual_error_Edn_percent_year3)/3

annual_error_Srr_percent_year1 <- (min(cumsum(medianGPP[1218:1512]))-min(cumsum(EL_RR_De_data_results$GPP_gC_m2_day[1218:1512])))/min(cumsum(EL_RR_De_data_results$GPP_gC_m2_day[1218:1512]))*100
annual_error_Srr_percent_year2 <- (min(cumsum(medianGPP[1513:1877]))-min(cumsum(EL_RR_De_data_results$GPP_gC_m2_day[1513:1877])))/min(cumsum(EL_RR_De_data_results$GPP_gC_m2_day[1513:1877]))*100
annual_error_Srr_percent_year3 <- (min(cumsum(medianGPP[1878:2243]))-min(cumsum(EL_RR_De_data_results$GPP_gC_m2_day[1878:2243])))/min(cumsum(EL_RR_De_data_results$GPP_gC_m2_day[1878:2243]))*100
annual_error_Srr_percent_year4 <- (min(cumsum(medianGPP[2244:2608]))-min(cumsum(EL_RR_De_data_results$GPP_gC_m2_day[2244:2608])))/min(cumsum(EL_RR_De_data_results$GPP_gC_m2_day[2244:2608]))*100
annual_error_Srr_percent_year5 <- (min(cumsum(medianGPP[2609:2871]))-min(cumsum(EL_RR_De_data_results$GPP_gC_m2_day[2609:2871])))/min(cumsum(EL_RR_De_data_results$GPP_gC_m2_day[2609:2871]))*100
ave_annual_error_Srr <- (annual_error_Srr_percent_year1+annual_error_Srr_percent_year2+annual_error_Srr_percent_year3+annual_error_Srr_percent_year4+annual_error_Srr_percent_year5)/5

annual_error_Stj_percent_year1 <- (min(cumsum(medianGPP[2872:3236]))-min(cumsum(EL_RR_De_data_results$GPP_gC_m2_day[2872:3236])))/min(cumsum(EL_RR_De_data_results$GPP_gC_m2_day[2872:3236]))*100
annual_error_Stj_percent_year2 <- (min(cumsum(medianGPP[3237:3602]))-min(cumsum(EL_RR_De_data_results$GPP_gC_m2_day[3237:3602])))/min(cumsum(EL_RR_De_data_results$GPP_gC_m2_day[3237:3602]))*100
annual_error_Stj_percent_year3 <- (min(cumsum(medianGPP[3603:3967]))-min(cumsum(EL_RR_De_data_results$GPP_gC_m2_day[3603:3967])))/min(cumsum(EL_RR_De_data_results$GPP_gC_m2_day[3603:3967]))*100
ave_annual_error_Stj <- (annual_error_Stj_percent_year1+annual_error_Stj_percent_year2+annual_error_Stj_percent_year3)/3

p1 <- ggplot(EL_RR_De_data_results[1:1217,], aes(medianGPP, GPP_gC_m2_day)) +
  geom_point() +
  stat_smooth(method = lm)+
  labs(x = "Mod", y="Obs")+
geom_text(x=-6.2, y=-0.3, label="(a)")+
geom_text(x=-5.2, y=-0.8, label="y=0.71x-1.36")+
  ## To make the plot look prettier
  theme_bw(base_size = 12) +
  theme(axis.line = element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(colour = "black"),
        panel.background = element_blank(),
        legend.position = "center") 
p2 <- ggplot(EL_RR_De_data_results[1218:2871,], aes(medianGPP, GPP_gC_m2_day)) +
  geom_point() +
  stat_smooth(method = lm)+
    labs(x = "Mod", y="Obs")+
  geom_text(x=-7.75, y=0, label="(b)")+
  geom_text(x=-5.75, y=-1, label="y=1.18x-0.53")+
  ## To make the plot look prettier
  theme_bw(base_size = 12) +
  theme(axis.line = element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(colour = "black"),
        panel.background = element_blank(),
        legend.position = "center") 
p3 <- ggplot(EL_RR_De_data_results[2872:3967,], aes(medianGPP, GPP_gC_m2_day)) +
  geom_point() +
  stat_smooth(method = lm)+
    labs(x = "Mod", y="Obs")+
  geom_text(x=-13, y=1, label="(c)")+
  geom_text(x=-10, y=0, label="y=0.77x-0.57")+
  ## To make the plot look prettier
  theme_bw(base_size = 12) +
  theme(axis.line = element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(colour = "black"),
        panel.background = element_blank(),
        legend.position = "center") 
grid.arrange(p1, p2, p3, nrow = 1)



saveRDS(EL_RR_De_data_results,file="Final_GPP_param.rds")
```


```{r}
#Run model on validation sites,
#First import datasets from other sites
LA1_data <- read.csv("data_sets/Validation sites/LA1_data_GPP_mod.csv", header=TRUE) %>% 
 dplyr::select(1:15) 
#Take out the extra first column
LA1_data<-LA1_data[ ,2:15]
MRM_data <- read.csv("data_sets/Validation sites/MRM_data_GPP_mod.csv", header=TRUE) %>% 
 dplyr::select(1:15) 
#Take out the extra first column
MRM_data<-MRM_data[ ,2:15]
PLM_data <- read.csv("data_sets/Validation sites/Plm_data_GPP_mod.csv", header=TRUE) %>% 
 dplyr::select(1:15) 
#Take out the extra first column
PLM_data<-PLM_data[ ,2:15]

```

```{r}
#run the model on all 10,000 sets and plot means and 95% CI for 3 validation sites
#Start with LA1

source('./PEPRMT_Scripts/PEPRMT_final_sys_CO2_GPP.R')

GPP_mod_LA1 <- NULL

LA1_data <- LA1_data[c("DOY", "DOY_disc", "TA", "WT_cm", "PAR_umol_m2_s",
                "Reco_gC_m2_d", "GPP_gC_m2_d", "EVI", "Season",
               "NEE_error", "wetland_age", "FPAR","LUE")]
#--loop for running model 10,000 times---
  for(t in 1:length(final_parameter_set[ ,1])) {

  
  #5. execute PEPRMT CH4
  y_model<- PEPRMT_final_sys_CO2_GPP(theta = final_parameter_set[t , ],
                           data = LA1_data)
  mod_result <- y_model
  GPP_mod_LA1 <- cbind(GPP_mod_LA1, mod_result)
  }

GPP_mod_LA1 <- as.data.frame(GPP_mod_LA1)

## Transpose data.frame so that columns are time points and rows are samples from posterior
GPP_mod_LA12 <- GPP_mod_LA1 %>%
  t() %>%
  as.data.frame() %>%
  slice(1:10000)

## Calculate median and 95% credible intervals
## Each of these objects are vectors of length 3967
medianGPP_LA1 <- apply(GPP_mod_LA12, 2, median)
cilGPP_LA1 <- apply(GPP_mod_LA12, 2, function(x) quantile(x, 0.025))
ciuGPP_LA1 <- apply(GPP_mod_LA12, 2, function(x) quantile(x, 0.975))

## Put the summary stats together, with column of time points
GPPmod_summary_LA1 <- data.frame(time = 1:length(medianGPP_LA1), 
                             median = medianGPP_LA1,
                             cil = cilGPP_LA1,
                             ciu = ciuGPP_LA1)

#For a ggplot figure with line and shaded region:
GPPModelPlot <- ggplot(GPPmod_summary_LA1, aes(x = time, y = median)) +
  geom_ribbon(aes(ymin = cil, ymax = ciu), fill = "grey70", alpha = 1) + # shaded region
  geom_line(color = "black") + # line
  ## To edit the x and y axes
  scale_x_continuous("Time") +
  scale_y_continuous("GPP") +
  ## To make the plot look prettier
  theme_bw(base_size = 12) +
  theme(axis.line = element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(colour = "black"),
        panel.background = element_blank(),
        legend.position = "none")
GPPModelPlot
```


```{r}
#run the model on all 10,000 sets and plot means and 95% CI for 3 validation sites
#MRM

source('./PEPRMT_Scripts/PEPRMT_final_sys_CO2_GPP.R')

GPP_mod_MRM <- NULL

MRM_data <- MRM_data[c("DOY", "DOY_disc", "TA", "WT_cm", "PAR_umol_m2_s",
                "Reco_gC_m2_d", "GPP_gC_m2_d", "EVI", "Season",
               "NEE_error", "wetland_age", "FPAR","LUE")]
#--loop for running model 10,000 times---
  for(t in 1:length(final_parameter_set[ ,1])) {

  
  #5. execute PEPRMT CH4
  y_model<- PEPRMT_final_sys_CO2_GPP(theta = final_parameter_set[t , ],
                           data = MRM_data)
  mod_result <- y_model
  GPP_mod_MRM <- cbind(GPP_mod_MRM, mod_result)
  }

GPP_mod_MRM <- as.data.frame(GPP_mod_MRM)

## Transpose data.frame so that columns are time points and rows are samples from posterior
GPP_mod_MRM2 <- GPP_mod_MRM %>%
  t() %>%
  as.data.frame() %>%
  slice(1:10000)

## Calculate median and 95% credible intervals
## Each of these objects are vectors of length 3967
medianGPP_MRM <- apply(GPP_mod_MRM2, 2, median)
cilGPP_MRM <- apply(GPP_mod_MRM2, 2, function(x) quantile(x, 0.025))
ciuGPP_MRM <- apply(GPP_mod_MRM2, 2, function(x) quantile(x, 0.975))

## Put the summary stats together, with column of time points
GPPmod_summary_MRM <- data.frame(time = 1:length(medianGPP_MRM), 
                             median = medianGPP_MRM,
                             cil = cilGPP_MRM,
                             ciu = ciuGPP_MRM)

#For a ggplot figure with line and shaded region:
GPPModelPlot <- ggplot(GPPmod_summary_MRM, aes(x = time, y = median)) +
  geom_ribbon(aes(ymin = cil, ymax = ciu), fill = "grey70", alpha = 1) + # shaded region
  geom_line(color = "black") + # line
  ## To edit the x and y axes
  scale_x_continuous("Time") +
  scale_y_continuous("GPP") +
  ## To make the plot look prettier
  theme_bw(base_size = 12) +
  theme(axis.line = element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(colour = "black"),
        panel.background = element_blank(),
        legend.position = "none")
GPPModelPlot
```


```{r}
#run the model on all 10,000 sets and plot means and 95% CI for 3 validation sites
#PLM
source('./PEPRMT_Scripts/PEPRMT_final_sys_CO2_GPP.R')

GPP_mod_PLM <- NULL

PLM_data <- PLM_data[c("DOY", "DOY_disc", "TA", "WT_cm", "PAR_umol_m2_s",
                "Reco_gC_m2_d", "GPP_gC_m2_d", "EVI", "Season",
               "NEE_error", "wetland_age", "FPAR","LUE")]
#--loop for running model 10,000 times---
  for(t in 1:length(final_parameter_set[ ,1])) {

  
  #5. execute PEPRMT CH4
  y_model<- PEPRMT_final_sys_CO2_GPP(theta = final_parameter_set[t , ],
                           data = PLM_data)
  mod_result <- y_model
  GPP_mod_PLM <- cbind(GPP_mod_PLM, mod_result)
  }

GPP_mod_PLM <- as.data.frame(GPP_mod_PLM)

## Transpose data.frame so that columns are time points and rows are samples from posterior
GPP_mod_PLM2 <- GPP_mod_PLM %>%
  t() %>%
  as.data.frame() %>%
  slice(1:10000)

## Calculate median and 95% credible intervals
## Each of these objects are vectors of length 3967
medianGPP_PLM <- apply(GPP_mod_PLM2, 2, median)
cilGPP_PLM <- apply(GPP_mod_PLM2, 2, function(x) quantile(x, 0.025))
ciuGPP_PLM <- apply(GPP_mod_PLM2, 2, function(x) quantile(x, 0.975))

## Put the summary stats together, with column of time points
GPPmod_summary_PLM <- data.frame(time = 1:length(medianGPP_PLM), 
                             median = medianGPP_PLM,
                             cil = cilGPP_PLM,
                             ciu = ciuGPP_PLM)

#For a ggplot figure with line and shaded region:
GPPModelPlot <- ggplot(GPPmod_summary_PLM, aes(x = time, y = median)) +
  geom_ribbon(aes(ymin = cil, ymax = ciu), fill = "grey70", alpha = 1) + # shaded region
  geom_line(color = "black") + # line
  ## To edit the x and y axes
  scale_x_continuous("Time") +
  scale_y_continuous("GPP") +
  ## To make the plot look prettier
  theme_bw(base_size = 12) +
  theme(axis.line = element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(colour = "black"),
        panel.background = element_blank(),
        legend.position = "none")
GPPModelPlot
```


```{r}

## Hard to see the CI 
## LA1 Plot
LA1_data$GPP_mod_final <- GPPmod_summary_LA1$median
LA1_data$cil <- GPPmod_summary_LA1$cil
LA1_data$ciu <- GPPmod_summary_LA1$ciu

la1<-ggplot(LA1_data, aes(DOY)) +
  geom_ribbon(aes(ymin = cil, ymax = ciu), fill = "grey50", alpha = 1) + # shaded region
  geom_line(aes(x = DOY, y = GPP_mod_final))+
  geom_line(aes(y = GPP_gC_m2_d*-1), color = "red")+
  ## To edit the x and y axes
  #scale_x_continuous("") +
  #scale_y_continuous("") +
  labs(x = "", y="          ") +
  geom_text(x=275, y=-0.5, label="(a)")+
  ## To make the plot look prettier
  theme_bw(base_size = 12) +
  theme(axis.line = element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(colour = "black"),
        panel.background = element_blank(),
        legend.position = "center")


## MRM Plot
MRM_data$GPP_mod_final <- GPPmod_summary_MRM$median
MRM_data$cil <- GPPmod_summary_MRM$cil
MRM_data$ciu <- GPPmod_summary_MRM$ciu

mrm<-ggplot(MRM_data, aes(DOY)) +
  geom_ribbon(aes(ymin = cil, ymax = ciu), fill = "grey50", alpha = 1) + # shaded region
  geom_line(aes(y = GPP_mod_final))+
  geom_line(aes(y = GPP_gC_m2_d, color = "red"))+
 
  ## To edit the x and y axes
  #scale_x_continuous("") +
  #scale_y_continuous("") +
  labs(x = "", y=bquote('GPP '~ (gC ~ m^-2 ~ d^-1))) +

  geom_text(x=-5, y=-2, label="(b)")+
  ## To make the plot look prettier
  theme_bw(base_size = 12) +
  theme(axis.line = element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(colour = "black"),
        panel.background = element_blank(),
        legend.position = "center") 

## Plm Plot
PLM_data$GPP_mod_final <- GPPmod_summary_PLM$median
PLM_data$cil <- GPPmod_summary_PLM$cil
PLM_data$ciu <- GPPmod_summary_PLM$ciu

plm<-ggplot(PLM_data, aes(DOY)) +
  geom_ribbon(aes(ymin = cil, ymax = ciu), fill = "grey50", alpha = 1) + # shaded region
  geom_line(aes(y = GPP_mod_final))+
  geom_line(aes(y = GPP_gC_m2_d, color = "red"))+
  ## To edit the x and y axes
  #scale_x_continuous("") +
  #scale_y_continuous("") +
  labs(x = "Continuous day of year", y="          ") +
  geom_text(x=100, y=-2, label="(c)")+
  ## To make the plot look prettier
  theme_bw(base_size = 12) +
  theme(axis.line = element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(colour = "black"),
        panel.background = element_blank(),
        legend.position = "center") 

grid.arrange(la1, mrm, plm, ncol=1, nrow =3)
```



```{r}
#Run stats on final model results

LA1_data<-Final_GPP_valid[1:426,]
PLM_data<-Final_GPP_valid[1158:1357,]


RMSE_GPP_mod_LA1 <- rmse(LA1_data$GPP_mod_final, LA1_data$GPP_gC_m2_d*-1)
RMSE_GPP_mod_PLM <- rmse(PLM_data$GPP_mod_final, PLM_data$GPP_gC_m2_d)

#Normalized RMSE dimensionless metric of accuracy of model against SD of obs 
SD_GPP_LA1 <-sd(LA1_data$GPP_gC_m2_d*-1)
SD_GPP_PLM <- sd(PLM_data$GPP_gC_m2_d)

N_RMSE_GPP_mod_LA1 <- RMSE_GPP_mod_LA1/(SD_GPP_LA1)
N_RMSE_GPP_mod_PLM <- RMSE_GPP_mod_PLM/SD_GPP_PLM

#Pearson's correlation coefficient r
r_LA1 <- cor(LA1_data$GPP_gC_m2_d*-1, LA1_data$GPP_mod_final)
#r_MRM <- cor(MRM_data$GPP_gC_m2_d, MRM_data$GPP_mod_final)
r_PLM <- cor(PLM_data$GPP_gC_m2_d, PLM_data$GPP_mod_final)

model_la1 <- lm(GPP_gC_m2_d*-1 ~ GPP_mod_final, data=LA1_data)
summary(model_la1)
model_mrm <- lm(GPP_gC_m2_d ~ GPP_mod_final, data=MRM_data)
summary(model_mrm)
model_plm <- lm(GPP_gC_m2_d ~ GPP_mod_final, data=PLM_data)
summary(model_plm)

#Annual Error
#LA has a little more than a year, but I'll just lump it all together
annual_error_LA1_year1 <- (tail(cumsum(LA1_data$daily_gpp_mod),1)-tail(cumsum(LA1_data$GPP_gC_m2_d*-1),1))

# annual_error_MRM_percent_year1 <- (min(cumsum(MRM_data$GPP_mod_final[1:366]))-min(cumsum(MRM_data$GPP_gC_m2_d[1:366])))/
#   min(cumsum(MRM_data$GPP_gC_m2_d[1:366]))*100
# annual_error_MRM_percent_year2 <- (min(cumsum(MRM_data$GPP_mod_final[367:731]))-min(cumsum(MRM_data$GPP_gC_m2_d[367:731])))/
#   min(cumsum(MRM_data$GPP_gC_m2_d[367:731]))*100
# ave_annual_error_MRM <- (annual_error_MRM_percent_year1+annual_error_MRM_percent_year2)/2

annual_error_PLM_year1 <- (tail(cumsum(PLM_data$daily_gpp_mod),1)-tail(cumsum(PLM_data$GPP_gC_m2_d),1))

Overall_annual_ave_error <- (annual_error_LA1_year1+annual_error_PLM_year1)/2





p1 <- ggplot(LA1_data, aes(GPP_mod_final, GPP_gC_m2_d*-1)) +
  geom_point() +
  stat_smooth(method = lm)+
  labs(x = "Mod", y="Obs")+
geom_text(x=-2, y=0, label="(a)")+
geom_text(x=-0.75, y=-3, label="y=0.6x-0.32")+
  ## To make the plot look prettier
  theme_bw(base_size = 12) +
  theme(axis.line = element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(colour = "black"),
        panel.background = element_blank(),
        legend.position = "center") 
p2 <- ggplot(MRM_data, aes(GPP_mod_final, GPP_gC_m2_d)) +
  geom_point() +
  stat_smooth(method = lm)+
    labs(x = "Mod", y="Obs")+
  geom_text(x=-7, y=1, label="(b)")+
  geom_text(x=-5.75, y=0, label="y=1.7x-0.17")+
  ## To make the plot look prettier
  theme_bw(base_size = 12) +
  theme(axis.line = element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(colour = "black"),
        panel.background = element_blank(),
        legend.position = "center") 
p3 <- ggplot(PLM_data, aes(GPP_mod_final, GPP_gC_m2_d)) +
  geom_point() +
  stat_smooth(method = lm)+
    labs(x = "Mod", y="Obs")+
  geom_text(x=-7.5, y=-0, label="(c)")+
  geom_text(x=-6, y=-0.5, label="y=1.35x-0.16")+
  ## To make the plot look prettier
  theme_bw(base_size = 12) +
  theme(axis.line = element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(colour = "black"),
        panel.background = element_blank(),
        legend.position = "center") 
grid.arrange(p1, p2, p3, nrow = 1)



```






```{r}
saveRDS(EL_RR_De_data_results,file="Final_GPP_param.rds")
saveRDS(LA1_MRM_PLM_data_results,file="Final_GPP_valid.rds")

#Export final GPP model results and add into file for Reco modeling
write_csv(Final_GPP_param,"data_sets/final_GPP_model_results.csv")

```

```{r}
#FINAL GPP FIGURE WITH ALL PARAM AND VALIDATION SITES NO MRM ##########################################

#Load Final_GPP_valid.rds and Final_GPP_param.rds

update_geom_defaults("text", list(size = 2.5))

edn<-ggplot(Final_GPP_param[1:1217,], aes(Day_of_year)) +
    geom_line(aes(y = GPP_gC_m2_day), color = "red", size = 0.2)+
  geom_ribbon(aes(ymin = cil, ymax = ciu), fill = "grey50", alpha = 1) + # shaded region
  geom_line(aes(y = GPP_mod_final), size = 0.2)+
  labs(x = "", y=bquote('GPP' ~ (g~ C-CO[2] ~ m^-2 ~ d^-1))) +
    ylim(-10, 5)+
geom_text(x=-Inf, y=Inf, label="(a) US-EDN",hjust = 0, vjust = 1)+
  ## To make the plot look prettier
  theme_bw(base_size = 7) +
  theme(axis.line = element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        legend.position = "center",
        aspect.ratio=0.25)
#edn<- edn + scale_y_continuous(
  #labels = scales::number_format(accuracy = 1))


#Rush Ranch
RR<-ggplot(Final_GPP_param[1218:2871,], aes(Day_of_year)) +
    geom_line(aes(y = GPP_gC_m2_day), color = "red", size=0.2)+
  geom_ribbon(aes(ymin = cil, ymax = ciu), fill = "grey50", alpha = 1) + # shaded region
  geom_line(aes(y = GPP_mod_final),size=0.2)+
  labs(x = "", y=bquote('GPP' ~ (g~ C-CO[2] ~ m^-2 ~ d^-1)))+
    ylim(-15, 5)+
geom_text(x=-Inf, y=Inf, label="(c) US-Srr",hjust = 0, vjust = 1)+
  ## To make the plot look prettier
  theme_bw(base_size = 7) +
  theme(axis.line = element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        legend.position = "center",
        aspect.ratio=0.25) 
#RR<- RR + scale_y_continuous(
 # labels = scales::number_format(accuracy = 1))

#Delaware
Stj<-ggplot(Final_GPP_param[2872:3967,], aes(Day_of_year)) +
    geom_line(aes(y = GPP_gC_m2_day), color = "red",size=0.2)+
  geom_ribbon(aes(ymin = cil, ymax = ciu), fill = "grey50", alpha = 1) + # shaded region
  geom_line(aes(y = GPP_mod_final),size=0.2)+
  labs(x = "", y=bquote('GPP' ~ (g~ C-CO[2] ~ m^-2 ~ d^-1))) +
geom_text(x=-Inf, y=Inf, label="(e) US-StJ",hjust = 0, vjust = 1)+
      ylim(-15, 5)+
  ## To make the plot look prettier
  theme_bw(base_size = 7) +
  theme(axis.line = element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        legend.position = "center",
        aspect.ratio=0.25) 
#Stj<- Stj + scale_y_continuous(
  #labels = scales::number_format(accuracy = 1))

p1 <- ggplot(Final_GPP_param[1:1217,], aes(GPP_mod_final, GPP_gC_m2_day)) +
  geom_point(size=0.5) +
  stat_smooth(method = lm)+
  labs(x = "Mod", y="Obs")+
geom_text(x=-Inf, y=Inf, label="(b) y=0.71x-1.36",hjust = 0, vjust = 1)+
  xlim(-5,0)+
  ylim(-6,2)+
   geom_abline(intercept = 0, color="red")+
  ## To make the plot look prettier
  theme_bw(base_size = 7) +
  theme(axis.line = element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        legend.position = "center",
        aspect.ratio=0.75)

p2 <- ggplot(Final_GPP_param[1218:2871,], aes(GPP_mod_final, GPP_gC_m2_day)) +
  geom_point(size=0.5) +
  stat_smooth(method = lm)+
    labs(x = "Mod", y="Obs")+
geom_text(x=-Inf, y=Inf, label="(d) y=1.18x-0.53",hjust = 0, vjust = 1)+
   # xlim(0,50)+
  ylim(-15,2)+
   geom_abline(intercept = 0, color="red")+
  ## To make the plot look prettier
  theme_bw(base_size = 7) +
  theme(axis.line = element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        legend.position = "center",
        aspect.ratio=0.75)

p3 <- ggplot(Final_GPP_param[2872:3967,], aes(GPP_mod_final, GPP_gC_m2_day)) +
  geom_point(size=0.5) +
  stat_smooth(method = lm)+
    labs(x = "Mod", y="Obs")+
geom_text(x=-Inf, y=Inf, label="(f) y=0.77x-0.57",hjust = 0, vjust = 1)+
  #  xlim(0,500)+
  ylim(-15,2)+
   geom_abline(intercept = 0, color="red")+
  ## To make the plot look prettier
  theme_bw(base_size = 7) +
  theme(axis.line = element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        legend.position = "center",
        aspect.ratio=0.75) 

la1<-ggplot(Final_GPP_valid[1:426,], aes(DOY)) +
    geom_line(aes(y = GPP_gC_m2_d*-1), color = "red",size=0.2)+
  geom_ribbon(aes(ymin = cil, ymax = ciu), fill = "grey50", alpha = 1) + # shaded region
  geom_line(aes(y = GPP_mod_final),size=0.2)+
  labs(x = "", y=bquote('GPP' ~ (g~ C-CO[2] ~ m^-2 ~ d^-1))) +
    ylim(-5, 5) +
geom_text(x=-Inf, y=Inf, label="(g) US-LA1",hjust = 0, vjust = 1)+
  ## To make the plot look prettier
  theme_bw(base_size = 7) +
  theme(axis.line = element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        legend.position = "center",
        aspect.ratio=0.25)
#la1<- la1 + scale_y_continuous(
 # labels = scales::number_format(accuracy = 1))

## Plm Plot

plm<-ggplot(Final_GPP_valid[1158:1357,], aes(DOY)) +
    geom_line(aes(y = GPP_gC_m2_d), color = "red",size=0.2)+
  geom_ribbon(aes(ymin = cil, ymax = ciu), fill = "grey50", alpha = 1) + # shaded region
  geom_line(aes(y = GPP_mod_final),size=0.2)+
    labs(x = "Continuous day of year", y=bquote('GPP' ~ (g~ C-CO[2] ~ m^-2 ~ d^-1))) +
  ylim(-15, 5) +
geom_text(x=-Inf, y=Inf, label="(i) US-PLM",hjust = 0, vjust = 1)+
  ## To make the plot look prettier
  theme_bw(base_size = 7) +
  theme(axis.line = element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        legend.position = "center",
        aspect.ratio=0.25) 
#plm<- plm + scale_y_continuous(
  #labels = scales::number_format(accuracy = 1))

p4 <- ggplot(Final_GPP_valid[1:426,], aes(GPP_mod_final, GPP_gC_m2_d*-1)) +
  geom_point(size=0.5) +
  stat_smooth(method = lm)+
  labs(x = "Mod", y="Obs")+
geom_text(x=-Inf, y=Inf, label="(h) y=0.6x-0.32",hjust = 0, vjust = 1)+
  #xlim(0,50)+
  ylim(-5,2)+
   geom_abline(intercept = 0, color="red")+
  ## To make the plot look prettier
  theme_bw(base_size = 7) +
  theme(axis.line = element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        legend.position = "center",
        aspect.ratio=0.75) 

p5 <- ggplot(Final_GPP_valid[1158:1357,], aes(GPP_mod_final, GPP_gC_m2_d)) +
  geom_point(size=0.5) +
  stat_smooth(method = lm)+
    labs(x = "Mod", y="Obs")+
geom_text(x=-Inf, y=Inf, label="(j) y=1.35x-0.16",hjust = 0, vjust = 1)+
  #xlim(0,50)+
  ylim(-12,2)+
 geom_abline(intercept = 0, color="red")+
  ## To make the plot look prettier
  theme_bw(base_size = 7) +
  theme(axis.line = element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        legend.position = "center",
        aspect.ratio=0.75) 

GPP_final_figure <-ggarrange(edn, p1, RR, p2, Stj, p3, la1, p4, plm, p5, ncol=2, nrow=5,widths = c(5, 2))


ggsave("figures/GPP/GPP_final_figure.png", GPP_final_figure,units="in", width=5, height=6, dpi=700)

```